Deciding to Disclose

### 2015-09-14 model_description.tex
Remove 'this'
Nash footnote

A game, in the game theoretic sense, this can be any interaction where the result for one person is dependent on the actions of another. In this scenario, the result for the woman would seem dependent on whether the midwife chooses to refer them for specialist support (although naturally the reality can only be thought of in terms of risk mitigation), and conversely, the right choice for the midwife is somewhat contingent on what the woman is willing to tell them.

@@

\begin{figure}[H]
\sidecaption
\includegraphics[width=7cm]{figures/simplest_game}
\caption{A very simple two player game. The only time things in this very restricted world obviously end poorly, is if the woman asks for help but does not get any. This implies that a rational player would always refer if asked for help, and is indifferent otherwise - in other words, there are three possible Nash equilibriums.}
\label{fig:simplest_game}
\end{figure}

>>>>

A game, in the game theoretic sense, can be any interaction where the result for one person is dependent on the actions of another. In this scenario, the result for the woman would seem dependent on whether the midwife chooses to refer them for specialist support (although naturally the reality can only be thought of in terms of risk mitigation), and conversely, the right choice for the midwife is somewhat contingent on what the woman is willing to tell them.

@@

\begin{figure}[H]
\sidecaption
\includegraphics[width=7cm]{figures/simplest_game}
\caption{A very simple two player game. The only time things in this very restricted world obviously end poorly, is if the woman asks for help but does not get any. This implies that a rational player would always refer if asked for help, and is indifferent otherwise - in other words, there are three possible Nash equilibriums\footnote{A Nash equilibrium is a solution to a game between two or more players, where no player can gain from changing their move.}.}
\label{fig:simplest_game}
\end{figure}
